Towards End-user Web Scraping For Customization

### 2021-05-11 paper.tex
Preparing paper for publication

@@

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%% From HERE
\begin{CCSXML}
<ccs2012>
<concept>
<concept_id>10011007.10011006.10011066.10011069</concept_id>
<concept_desc>Software and its engineering~Integrated and visual development environments</concept_desc>
<concept_significance>500</concept_significance>
</concept>
</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
% To HERE

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{end-user programming, software customization, web scraping, programming by example}

@@

\hypertarget{acknowledgements}{%
\section{Acknowledgements}\label{acknowledgements}}

Thank you to Gloria Lin, Joshua Pollock, the members of MIT's Software
Design Group, the anonymous reviewers of PX/21 and the particpants of
PX/21 for providing valuable feedback on this work.

>>>>

%%% The following is specific to <Programming'21> Companion-PX and the paper
%%% 'Towards End-User Web Scraping for Customization'
%%% by Kapaya Katongo, Geoffrey Litt, and Daniel Jackson.
%%%
\setcopyright{rightsretained}
\acmPrice{}
\acmDOI{10.1145/3464432.3464437}
\acmYear{2021}
\copyrightyear{2021}
\acmSubmissionID{prog21pxmain-p5-p}
\acmISBN{978-1-4503-8986-0/21/03}
\acmConference[<Programming'21> Companion]{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming}{March 22--26, 2021}{Virtual, UK}
\acmBooktitle{Companion Proceedings of the 5th International Conference on the Art, Science, and Engineering of Programming (<Programming'21> Companion), March 22--26, 2021, Virtual, UK}

@@

%%
%% The code below is generated by the tool at http://dl.acm.org/ccs.cfm.
%% Please copy and paste the code instead of the example below.
%%
%% From HERE
\begin{CCSXML}
<ccs2012>
   <concept>
       <concept_id>10003120.10003121.10003124.10010868</concept_id>
       <concept_desc>Human-centered computing~Web-based interaction</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
   <concept>
       <concept_id>10011007.10011006.10011066.10011069</concept_id>
       <concept_desc>Software and its engineering~Integrated and visual development environments</concept_desc>
       <concept_significance>500</concept_significance>
       </concept>
 </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Human-centered computing~Web-based interaction}
\ccsdesc[500]{Software and its engineering~Integrated and visual development environments}
% To HERE

%%
%% Keywords. The author(s) should pick words that accurately describe
%% the work being presented. Separate the keywords with commas.
\keywords{software customization, browser extensions, end-user programming, spreadsheets, web scraping}

@@

\section*{Acknowledgments}
Thank you to Gloria Lin, Joshua Pollock, the members of MIT's Software Design Group,
the anonymous reviewers of PX/21 and the particpants of PX/21 for providing valuable
feedback on this work. The authors gratefully acknowledge the support of the CNS division of the National Science Foundation
through award number 1801399.
